---
title: 'Homework 5: Iteration'
author: "Kimberly Lopez"
date: "2024-11-06"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)
library(broom)
library(dplyr)
```

```{r}
set.seed(5)
```

# Problem 1 

# Problem 2

For one randomly generated sample of n=30, with mean = 0, and sd= 5, run a t.test() and return the estimate & p-value: 
```{r}
sim_data = 
    tibble(
    x = rnorm (30, mean= 0, sd= 5))

t.test(sim_data)|>
  broom::tidy()|>
  select(estimate,p.value)
```


Function for performing a one-sample t-test and returning the estimate & p-value:
```{r}

sim_t_test = function ( n , mu= 0, sigma =5) {
  
  sim_data = 
    tibble(
    x = rnorm (n, mean= mu, sd= sigma))
  
  sim_data|>
    t.test()|>
    broom::tidy()|>
    select(estimate, p.value)
  
}

sim_t_test(n=30)
```
For 5000 datasets: when mu=1
```{r}
output = vector("list", 5000)

for (i in 1:5000) {
  output[[i]] = sim_t_test(n=30)
}

sim_results_mu1 = bind_rows(output)

sim_results_mu1
```

Function for calculating power: known as the proportion of times the null was rejected 

- Use after binding all simulations 
```{r}

sim_power = function ( data) {
  
  data|>
   filter(p.value < 0.05) |>
  summarize(
    power = n() / nrow(data), 
    mu = unique(mu))
  
}

```


Function that run the 5000 sample for loop updating mu for mu= 1,2,3,4,5,6 
```{r}
sim_results=list()

for (mu_val in 1:6) {
  

  output= vector("list", 5000)
  for (i in 1:5000) {
    output[[i]] = sim_t_test(n = 30, mu = mu_val)
  }
  
  sim_results[[mu_val]]= bind_rows(output) |>
    mutate(mu = mu_val)  
}

```

```{r}
sim_results
```


```{r}
output= map_dfr(sim_results, sim_power)|>
  bind_rows()

output 
output|>
  ggplot(aes(x=mu, y = power))+
  geom_point()
```

The scatter plot of the power of the test associated with a given mu value  increases as mu increases. With a fixed sample size of n=30 and standard deviation = 5, increasing the magnitude of mu increases the observed power of the test. The larger values of mu create a greater difference from the null hypothesis, making it easier to detect a true effect.

# Problem 3 


